### 2022-05-06 project_Luis/paper.tex
Luis project

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{./LHCcomplex.png}
  \caption{Diagram of the LHC accelerator complex located near Geneva, Switzerland. The complex consists of three accelerator stages: the proton (p) or lead (Pb) source, the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring. Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors  \cite{wiki:xxx}.} % Mobs:2684277
  \label{figure5}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{./LHC-cpx-book.png}
  \caption{Diagram of the LHC accelerator complex located near Geneva, Switzerland. The complex consists of the accelerator stages: Linear accelerator 2 (LINAC2; linear accelerator in which the protons are accelerated in bunches) , the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring. Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors \cite{Zinser2018}.} % \cite{wiki:xxx}.} % Mobs:2684277
  \label{figure5}
\end{figure}
